Bayesian models for NLA 2017 $N_2O$ survey data

### 2023-03-03 scripts/NLA_N2O_models.Rmd

---
title: "Bayesian models for NLA 2017 $N_2O$ survey data"
author: "Roy Martin, Jake Beaulieu, Michael McManus"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: show
    font_size: 14
    number_sections: yes
    theme: simplex
bibliography: RWM_Endnote_Library.bib
link-citations: yes
editor_options:
  chunk_output_type: inline
---

>>>>

---
title: "Bayesian models for NLA 2017 $N_2O$ survey data"
author: "Roy Martin, Jake Beaulieu, Michael McManus"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    toc: yes
    toc_depth: 4
    toc_float: yes
    code_folding: show
    font_size: 14
    number_sections: yes
    theme: simplex
bibliography: RWM_Endnote_Library.bib
link-citations: yes
editor_options:
  chunk_output_type: inline
---
